Medical Concept Extraction

### 2012-12-17 paper/paper.tex
Updating More Data subsection.

>>>>

Additionally, the training data is derived from clinical notes originating at Beth Israel Deaconess and Partners Healthcare. It would be interesting to test our system against data from health centers outside the Boston area which have differently organized notes to see if our system is able to generalize well. Because many of our features avoided encoding language structure that appeared in the training data when possible, we expect this generalization would be relatively good assuming that the vocabulary used in an alternate test set was similar to our training set. However, this could very easily not be the case.
